Bioverse: Origins of Life

### 2024-09-17 src/tex/ms.tex
motivate semi-analytical approach

\subsection{Semi-analytical approach}\label{sec:met-semianalytical}
First, we apply a Bayes Factor Design Analysis~\citep{Schoenbrodt2018} to assess the expected probabilities of obtaining true negative or true positive evidence for the hypothesis above, as well as the probability for misleading or inconclusive evidence, under idealized conditions.
This serves as a first-order estimate of the information content of a survey, before we take into account impacts from exoplanet demographics, sample selection, and survey strategy.

@@

For all survey simulations and hypothesis tests, we repeated the above in a Monte Carlo fashion to generate randomized ensembles of synthetic star and planet populations~\citep[compare][]{Bixel2021}.

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To test the UV~Threshold Hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All common Origin of Life scenarios require water as a solvent;
we thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their momentary \gls{HZ} during the above period.

>>>>

\subsection{Semi-analytical approach}\label{sec:met-semianalytical}
%First, we apply a Bayes Factor Design Analysis~\citep{Schoenbrodt2018}
We first assessed the expected probabilities of obtaining true negative or true positive evidence for the UV Threshold Hypothesis ($H_1$) above, as well as the probability for misleading or inconclusive evidence, under idealized conditions.
This serves as a first-order estimate of the information content of a survey, before we take into account impacts from exoplanet demographics, sample selection, and survey strategy.

@@

For all survey simulations and hypothesis tests, we repeated the above in a Monte Carlo fashion to generate randomized ensembles of synthetic star and planet populations~\citep[][]{Bixel2021}.

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To test the UV~Threshold Hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All common Origin of Life scenarios require water as a solvent;
we thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their host star's momentary \gls{HZ} during the above period.
This takes into account the evolution of the host star's luminosity and \gls{HZ} boundaries.
